A Mechanised Library for Generic (Co)Programming

### 2024-02-23 paper/paper.tex
more writing for section 5

@@

Another approach to certifying termination of nonstructurally recursive
functions is the use of \emph{sized types}. Sized types were introduced by
Hughes et al.\ as a way to track/verify various properties of recursive
programs, including productivity and termination~\cite{HughesPS96}. The core
idea of sized types is that types express bounds on the sizes of recursive data
structures. With this approach, algorithms are implemented in the standard
functional way, following the divide-and-conquer pattern of splitting, recurring,
and merging, with the addition of the data types being indexed by a static
approximation of the relative \emph{size}. An advantage of this approach is
that it allows for code to be written in a natural way.

This approach has been used to express nonstructurally recursive
algorithms in Agda: Copello et al.\ used sized types in a straightforward
formulation of mergesort~\cite{CopelloTB14}. Such an approach has also been used
in MiniAgda~\cite{abs-1202-3496}. A proposal exists to add sized types to
Coq as well~\cite{CHAN_2023}.

>>>>

\subsection{Program Calculation}

Within the domain of program optimization, program calculation serves as a
well-established programming technique aimed at deriving efficient programs from
their naive counterparts through systematic program transformation. This area
has been extensively explored over the years. Tesson et al.\ demonstrated the
efficacy of leveraging Coq to establish an approach for implementing a robust
system dedicated to verifying the correctness of program transformations for
functions that manipulate lists~\cite{10.1007/978-3-642-17796-5_10}. Murata and
Emoto went further and\ldots~\cite{10.1007/978-3-030-34175-6_11}

@@

Another approach to certifying termination of nonstructurally recursive
functions is the use of \emph{sized types}. Sized types were introduced by
Hughes et al.\ as a way to track/verify various properties of recursive
programs, including productivity and termination~\cite{HughesPS96}. The core
idea of sized types is that types express bounds on the sizes of recursive data
structures. With this approach, algorithms are implemented in the standard
functional way, following the divide-and-conquer pattern of splitting, recurring,
and merging, with the addition of the data types being indexed by a static
approximation of the relative \emph{size}. An advantage of this approach is
that it allows for code to be written in a natural way. There are costs, however.
Programs must be written in a way that accounts for the handling of size indexes,
and support for the size types must be added to the language.

This approach has been used to express nonstructurally recursive
algorithms in Agda: Copello et al.\ used sized types in a straightforward
formulation of mergesort~\cite{CopelloTB14}. Such an approach has also been used
in MiniAgda~\cite{abs-1202-3496}. A proposal exists to add sized types to
Coq as well, though it has not yet been adopted~\cite{CHAN_2023}.
